\section{Future Work}

Currently, our tool uses Oyente, Mythril, and SmartCheck to analyze Solidity smart contracts, then reports the bugs found within. These three give us the widest coverage while maintaining accuracy. This succeeds in allowing Solidity developers in an easy-to-use interface and gives a variety of results. We also allow developers to flag certain code snippets to be more important. We have also expanded on our previous experiments by running on a wider variety of smart contracts. Two notable large contracts here (King of the Ether and Cryptokitties) are over 1,000 lines long. \\

Moving forward, we'd like to provide an easier method to allow updates for analyzers so they may easily adapt to future changes. Additionally, enabling developers to add their own testing suites would be useful as well. Since many smart contracts have similar crucial areas (e.g. authentication, external oracle, sending money, etc), perhaps we could recommend templates with secure design patterns to the developer depending on their code's errors. \\

For improving analysis tools, most tools often come up with false positive or negatives. Improving on accuracy would save time and developer effort. Furthermore, these tools are currently quite difficult to find. They are infrequently mentioned in official documentation and most new developers will not immediately think to look for these tools. As such, providing a Solidity IDE would be a promising way to quickly improve smart contract code quality, as they could embed testing suites by default. Overall, smart contracts have fantastic potential; improving code quality through better testing would quickly reduce the number of buggy contracts on the network, thus encouraging user growth!  

